Enhancing Adversarial Robustness for Deep Metric Learning

### 2021-11-18 appendix.tex
tex

@@

\noindent\textbf{I. Range of Hardness.}

@@

~\newline
\noindent\textbf{II. Parameters or Adjustable Items}

The only two adjustable items in HM are $H_\mathsf{S}$ and $H_\mathsf{D}$.
%
They are further discussed in the previous section in this supplementary
material (see the ``Performance-Sensitive Factors'' part of the previous
section).

Since PGD~\cite{madry} is adopted for optimizing the objective of HM, the
PGD parameters (including perturbation budget $\varepsilon$, maximum step
$\eta$, as well as step size $\alpha$) will also influence the result.
%
We use the parameter setting following the state-of-the-art
defense~\cite{robrank} for fair comparison.

In most experiments that demonstrate the effectiveness of our method, the
$\eta$ is set as $8$ because the ERS start to plateau with a larger $\eta$
according to our observation.

~\newline
\noindent\textbf{III. HM and ACT}

ACT~\cite{robrank} is proposed in order to address the ``misleading gradient''
and ``inefficient mini-batch exploitation'' problems.
%
HM does not push the embeddings towards arbitrary directions, and hence does
not suffer from both issues.
%
On the other hand, ACT does not perturb the anchor sample, and the same
can be done in HM.
%
When the anchor sample is unperturbed, adversarial training with HM leads to
a higher performance on benign examples but a lower robustness.
%
Unlike perturbing $(\mA, \mP, \mN)$ altogether, only perturbing $(\mP, \mN)$
leads to a weaker adversarial examples, and hence lower robustness.
%
Our first priority is to improve model robustness, so the case with fixed
anchor is omitted from manuscript to avoid complexity.

~\newline
\noindent\textbf{IV. Mixing HM[$\mathcal{R},\mathcal{M}$] and
HM[$\mathcal{S},\mathcal{M}$]}

@@

The parameters, namely $u$ and $\xi$ are discussed in the previous section
of this supplementary material, see ``Performance-Sensitive Factors''.

@@

In the manuscript, Linear Graduate Adversarial is demonstrated effective,
and more complicated choices are left for future work.
%
Here we provide two Non-linear Graduate Adversary examples, namely
$g_\mathsf{2}$ and $g_\mathsf{1/2}$, as follows:
%
\begin{align}
	g_\mathsf{2}(\cdot)   &= -\gamma \cdot (\bar{\ell}_{t-1})^{2}  &~ \in [-\gamma,0]\\
	g_\mathsf{1/2}(\cdot) &= -\gamma \cdot (\bar{\ell}_{t-1})^{1/2} &~ \in [-\gamma, 0]
\end{align}
%
Compared to LGA, $g_\mathsf{2}$ is more ``eager'' to result in strong adversarial
examples in the early phase of training, while $g_\mathsf{1/2}$ is more ``conservative''
in creating strong adversarial examples in the early phase of training
(adversarial examples from HM are stronger if the function value is closer to $0$).

\oo{experiments?}

>>>>

\begin{table*}[t]
\resizebox{\linewidth}{!}{
\setlength{\tabcolsep}{0.47em}
\renewcommand{\arraystretch}{1.1}%
\begin{tabular}{c|cc|cccc|ccccc|ccccc|c}
	\toprule
\multirow{2}{*}{\textbf{Dataset}} & \multirow{2}{*}{\textbf{Defense}} & \multirow{2}{*}{$\eta$} & \multicolumn{4}{c|}{\textbf{Benign Example}} & \multicolumn{10}{c|}{\textbf{White-Box Attacks for Robustness Evaluation}} & \multirow{2}{*}{\textbf{ERS$\uparrow$}}\tabularnewline
\cline{4-17} \cline{5-17} \cline{6-17} \cline{7-17} \cline{8-17} \cline{9-17} \cline{10-17} \cline{11-17} \cline{12-17} \cline{13-17} \cline{14-17} \cline{15-17} \cline{16-17} \cline{17-17}
 &  &  & R@1$\uparrow$ & R@2$\uparrow$ & mAP$\uparrow$ & NMI$\uparrow$ & CA+$\uparrow$ & CA-$\downarrow$ & QA+$\uparrow$ & QA-$\downarrow$ & TMA$\downarrow$ & ES:D$\downarrow$ & ES:R$\uparrow$ & LTM$\uparrow$ & GTM$\uparrow$ & GTT$\uparrow$ & \tabularnewline
 \midrule
\multirow{3}{*}{CUB} & HM{[}$\mathcal{S},g_{\mathsf{1/2}}${]} & 8 & 38.7 & 48.5 & 22.0 & 49.2 & 12.6 & 48.6 & 12.3 & 41.3 & 0.562 & 0.825 & 13.5 & 12.9 & 26.9 & 1.8 & 31.7\tabularnewline
& HM{[}$\mathcal{S},g_{\mathsf{LGA}}${]} & 8 & 38.0 & 48.3 & 21.8 & 49.3 & 12.7 & 46.4 & 11.6 & 39.9 & 0.567 & 0.783 & 16.8 & 11.9 & 27.9 & 1.4 & 32.4\tabularnewline
& HM{[}$\mathcal{S},g_{\mathsf{2}}${]} & 8 & 37.4 & 48.2 & 17.1 & 49.2 & 12.9 & 45.1 & 13.2 & 39.1 & 0.599 & 0.738 & 17.7 & 12.8 & 27.5 & 1.9 & 33.1\tabularnewline
\bottomrule
\end{tabular}}
	\caption{Non-linear Gradual Adversary Examples.}
	\label{tab:nonlinga}
\end{table*}

@@

\noindent\textbf{I. Adjustable Items}

The only two adjustable items in HM are $H_\mathsf{S}$ and $H_\mathsf{D}$.
%
They are discussed in the ``Performance-Sensitive Factors'' part of the
previous section.

~\newline
\noindent\textbf{II. Range of Hardness.}

@@

~\newline
\noindent\textbf{III. Mixing HM[$\mathcal{R},\mathcal{M}$] and
HM[$\mathcal{S},\mathcal{M}$]}

@@

\noindent\textbf{I. Parameters}

The parameters, namely $u$ and $\gamma$ are discussed in the previous section
of this supplementary material, see ``Performance-Sensitive Factors''.

The parameter $\xi$ in $g_\mathsf{B}$ is set as $0.1$, but it is not an important parameter.
%
The function $g_\mathsf{B}$ is only used for demonstrating that ``slightly
boosting the destination hardness can further increase ERS'' as discussed
in Sec.~3.1.

@@

In Sec.~3.2, more complicated designs are left for future work.
%
We provide two Non-linear Graduate Adversary examples, namely
$g_\mathsf{2}$ and $g_\mathsf{1/2}$, as follows:
%
\begin{align}
	g_\mathsf{2}(\cdot)   &= -\gamma \cdot (\bar{\ell}_{t-1})^{2}  &~ \in [-\gamma,0]\\
	g_\mathsf{1/2}(\cdot) &= -\gamma \cdot (\bar{\ell}_{t-1})^{1/2} &~ \in [-\gamma, 0]
\end{align}
%
Compared to LGA, $g_\mathsf{2}$ is more ``eager'' to result in strong adversarial
examples in the early phase of training, while $g_\mathsf{1/2}$ is more ``conservative''
in creating strong adversarial examples in the early phase of training
(adversarial examples from HM are stronger if the function value is closer to $0$).
%
The corresponding experiments can be found in \cref{tab:nonlinga}.

\oo{TODO}
